Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, \Sexpr{formatYear(startDate)}-\Sexpr{formatYear(endDate)}

### 2020-10-04 paper/nature-scirep-cover.tex
Fit cover on one page

\opening{\textbf{Dear \textit{Pediatrics} editor,}}

I am pleased to submit an original research article titled \textit{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013} by Ben Artin, Virginia E. Pitzer, an Daniel M. Weinberger for consideration for publication in \textit{Pediatrics}. The American Academy of Pediatrics makes recommendations about when to start prophylaxis against RSV. Aside from Florida, the recommended start date is the same for the entire US. Using county-level data from Connecticut, we considered whether a recommended start date that varies by state or county would provide any benefit compared with the national recommendation. We find that a state-specific prophylaxis regimen would confer a modest improvement over the current AAP-recommended regimen. This general approach could be used to evaluate the timing of prophylaxis in other states as well.

We believe that this manuscript is appropriate for publication by \textit{Pediatrics} because of the impact of RSV on infant hospitalizations, mortality, and morbidity, as well as the role of your audience in implementing RSV prophylaxis guidelines.

This manuscript has not been published elsewhere and is not under consideration for publication elsewhere. Should it be published in \textit{Pediatrics}, it will not be published elsewhere without the editors' consent. Preprint is available on medRxiv at \url{https://doi.org/10.1101/2020.07.13.20152215}. All authors have participated in the concept and design, analysis and interpretation of data, and drafting or revising of the manuscript, have approved the manuscript as submitted, and are responsible for the reported research.

The same data was used in: Noveroske Douglas Brian. Respiratory syncytial virus in Connecticut: Predictors of seasonal epidemic timing \textit{Public Health Theses}. 2016.

>>>>

\opening{\textbf{Dear \textit{Scientific Reports} editor,}}

I am pleased to submit an original research article titled \textit{Assessment and optimization of respiratory syncytial virus prophylaxis in Connecticut, 1996-2013} by Ben Artin, Virginia E. Pitzer, an Daniel M. Weinberger for consideration for publication in \textit{Scientific Reports}. The American Academy of Pediatrics makes recommendations about when to start prophylaxis against respiratory syncytial virus (RSV). Aside from Florida, the recommended start date is the same for the entire US. Using county-level data from Connecticut, we considered whether a recommended start date that varies by state or county would provide any benefit compared with the national recommendation. We find that a state-specific prophylaxis regimen would confer a modest improvement over the current AAP-recommended regimen. This general approach could be used to evaluate the timing of prophylaxis in other states as well.

We believe that this manuscript is appropriate for publication by \textit{Scientific Reports} because of the impact of RSV on infant hospitalizations, mortality, and morbidity, as well as the role of your audience in setting and carrying out RSV prophylaxis guidelines.

This manuscript has not been published elsewhere and is not under consideration for publication elsewhere. It has not been previously discussed with an EBM. Should it be published in \textit{Scientific Reports}, it will not be published elsewhere without the editors' consent. Preprint is available on medRxiv at \url{https://doi.org/10.1101/2020.07.13.20152215}. All authors have participated in the concept and design, analysis and interpretation of data, and drafting or revising of the manuscript, have approved the manuscript as submitted, and are responsible for the reported research.
